Simulation and visualization framework for selecting appropriate urban-scale climate mitigation and adaptation strategies

### 2021-02-01 manuscript_wesbrook-bigmacc_BS2021.tex

\section*{Abstract}	% Section headings need to be upper and lower case.
\addtocounter{section}{1}
At present mitigation and adaptations strategies compete for constrained resources within a future of uncertain climate impacts. Meeting decarbonisation goals while implementing robust and resilient adaptation strategies requires an analysis structure that can account for uncertainty as well as depict how the intermingling of strategies may hinder or benefit the ultimate trajectory of actions. The marginal abatement cost curve (MACC) is an indispensable tool for planning mitigation pathways, but has historically not relied upon robust experimental analysis making it notional at best nor has it included a view of adaptation pathways. This study utilizes a newly developed, medium-density residential community in Vancouver, British Columbia, Canada (15,000 residents) as a case study for developing a pathway-based MACC. Multiple mitigation and adaptation measures are modeled individually and through exhaustive combination to test their sensitivity on marginal abatement cost and residual cost of climate change. Several visualizations are created to demonstrate several ways of analyzing the resulting large set of data.

@@

This study integrates several climate adaptation strategies into the urban-scale energy simulation process. Adaptation strategies are evaluated on the basis of marginal costs of mitigation \textit{and} adaptation, vis-a-vis the influence of individual design strategies on the resilience of the urban development to expectec climate change.

This study will simulate the performance of eight climate mitigation and adaptation strategies alongside one urban development trajectory and two climate change scenarios. The simulations will be also carried out at two individual time periods (2050 and 2080), for a case study community in southwestern Canada: Wesbrook Village, Vancouver, British Columbia (BC). A baseline urban building energy model (UBEM) was created to represent the development of the community to-date.

The outline of this study is as follows. SecitonXX does..... Seciton XX does....

@@

% \begin{figure}
%     \centering
%     \includegraphics{}
%     \caption{The baseline UBEM for Wesbrook Village in BC.}
%     \label{fig:wesbrook_base}
% \end{figure}

@@

\begin{table*}[ht]
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
    \caption{Each strategy as it was applied in the simulations.}
    \footnotesize
    \label{tab:strategies}
    \centering
    \begin{tabularx}{\textwidth}{|X|X|X|}
        \hline
        \bf{Strategy} & \bf{Description} & \bf{Scale} \\
        \hline
        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings \\
        \hline
        Green Roof & Install green roofs for insulative, albedo, and heat gain benefits. & All Buildings \\
        \hline
        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings \\
        \hline
        Passive House & Require passive house building codes for envelope. & New Buildings \\
        \hline
        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings \\
        \hline
        Mass Timber & Construction must utilize mass timber. & New Buildings \\
        \hline
        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings \\
        \hline
        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings \\
        \hline
    \end{tabularx}
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table*}

@@

The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{cwec_2016} was morphed, following the algorithms set out by \citet{belcher_constructing_2005} and expanded upon by \citet{jentsch_climate_2008}. Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios. These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
defined in \citet{oneill_roads_2017}. Four morphed climate files are produced and described in Figure \ref{fig:weatherfiles}.

@@

Adaptation was considered as the capacity of a building to remain in its comfort threshold while also mitigating carbon emissions. The threshold is set to setpoints of the buildings, which are in a majority 21C for heating and 26C for cooling - except where changed by the first strategy. The deviation from the threshold is measured as the percent change from the baseline in \textit{total hours outside of the threshold} for each iteration. For instance if in the baseline case \textit{total hours outside of threshold} are 2000 and in an experiment the \textit{total hours outside of threshold} are 1500, we have seen a 25\% decrease.

@@

\subsection*{Total Annualized Cost}
Components and technology costs was gathered through several data sources, \citep{noauthor_cpcn_2014,schlueter_3for2_2016,salasovich_energy_2016,kegel_life_nodate,gordian_rsmeans_2020}. The authors recognize that cost is a highly uncertain data point to incorporate into building energy models. While the entire capital and operating cost of each building do not encompass the cost of components and technologies that are affected by strategies are included, making the calculation of net cost between the base-case and an intervention plausible. Cost is assessed as the 30-year total annualized cost (TAC) from within the City Energy Analyst, applying a 5\% discount rate.

\subsection*{Operational and embodied carbon}
Operational carbon is taken as the carbon emitted over a 30 year period from each building as a result of energy consumption for plug-load, heating and cooling, and ventilation service. BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}. The district heating provider intends for the system tobe  fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and electric heat pumps. This system was previously modelled in \citet{mccarty_accepted_2020}. Its carbon intensity was estimated to be between an annual average of 10.8 and 180.0 kgCO2e/kWh. The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps. Figure \ref{fig:district_heat_explainer} describes a baseline case of performance with the system. Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{noauthor_infrastructure_2014}.

@@

%---------------------------------------------------------------------------------------
\section*{Results}
\begin{figure}[hbpt]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
    \caption{Comparing the demand on the partially natural gas fed district heat system across the baseline scenarios in the end of century best- (SSP126) and worst-case (SSP585) scenarios. The highlighted gap between the two curves shows where less natural gas was used in the SSP585 scenario.}
    \label{fig:compare_district}
\end{figure}

@@

Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario. For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier. The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%. The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented. These charts can inform the creation of a \textit{true} MACC by informing which strategy set is chosen based on not only marginal abatement cost, but also the adaptation metric.

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}. Figure \ref{fig:true_macc_both} describes how each strategy contributes to the overall decrease in emissions. The MACC is shown in Figure \ref{fig:true_macc_both} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction. This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity. The majority of the abatement can be attributed to the heat pump strategy, removing natural gas from the fuel mix, while the other strategies can be said to lending to adaptability. This point about the fuel mix will be returned to more in the discussion, but raises that question about how to affordably meet zero-carbon targets after fuel-switching has been achieved. This scenario only achieves 67\% emissions reduction over the baseline by 2080.

@@

\begin{figure}[t]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.50]{figures/pareto_plots_585_box.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:pareto_plot}
\end{figure}

%---------------------------------------------------------------------------------------
\section*{Discussion}
The use of MACCs, \textit{true} and \textit{illustrative}, offers urban scale energy and development planners a way to compare different types of interventions for their merit as adaptation and mitigation interventions. This analysis is robust in that it simulates the technical and financial interaction of the proposed strategies under multiple climate change pathways and following different development trajectories. The first limitation lies in the not-so-explicit temporal interaction of the interventions. Each building was modeled as having its own unique construction and retrofit dates, which contribute to the emissions and total annualized cost profile for each run of the district energy model. While unique in their start and end date they are all set on a 30-year time horizon for all elements replacement. For some building technologies this may be a realistic time horizon for design-life, for many others it is not. Future efforts need to consider equipment and technology replacements more actively while also engaging the temporal simulation steps at more fine scales, possibly ten-years.

\subsection*{Strategy choice}
A major limitation in the framework underpinning this study is the finite space of strategy choice. We test eight strategies here that are applied generally across the district. This may not always be a problem if prior to the study a strategy evaluation study is conducted or subject-matter experts are brought in to help establish priors. Future efforts need to be more precise with strategy implementation based on building or site need.

\subsection*{Abatement after fuel-switching}
The context for this study sets up an interesting proposition within BC. The electrical grid is majority hydroelectric. Emissions within the building sector are therefore driven by natural gas use, either on site or within district systems. The two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition the use of natural gas must be eliminated. This however raises the point of how abatement should continua once the significant reductions are made and systems are then relying on a near-carbon free grid. Future building code intends for new buildings to be net-zero \textit{energy} ready, but this study showed in testing rooftop photovoltaic that for this type of density, just rooftop panels are not going to generate significant amounts of energy or contribute to emissions reductions; in the worst-case climate scenario rooftop panels alone reduced emissions by 4.4\%.

Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}. This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.

%---------------------------------------------------------------------------------------
\section*{Conclusion}
In this study the output of 1024 different urban building energy simulations was discussed in the context of use marginal abatement cost curves and complimentary visualizations to make decisions regarding mitigation and adaptation planning for a medium-density community in Vancouver, British Columbia. The simulations were differing combinations of development completeness of the community, climate change pathway (between best- and worst-case scenarios), and eight mitigation and adaptation strategies.

The resulting MACCs were created from two perspectives. First the \textit{illustrative} MACCs (Figures \ref{fig:MACC_threshold} and \ref{fig:MACC_budget}) provide general guidance on choosing sets of strategies to achieve mitigation under different planning constraints. The \textit{true} MACCs (Figure \ref{fig:true_macc_both}) reveal how the individual strategies within a set interact to technically and financially to ultimately abate a certain amount of carbon. The candidate for the one of the \textit{true} MACCs was selected based on a mixture of adaptation and mitigation criteria using a plot of pareto optimums (Figure \ref{fig:pareto_plot}). This enables planners to begin to assess adaptation targets alongside abatement.

>>>>

\section*{Abstract}	% Section headings need to be upper and lower case.
\addtocounter{section}{1}
At present mitigation and adaptations strategies compete for constrained resources within a future of uncertain climate impacts. Meeting decarbonisation goals while implementing robust and resilient adaptation strategies requires an analysis structure that can account for uncertainty as well as depict how the intermingling of strategies may hinder or benefit the ultimate trajectory of actions. The marginal abatement cost curve (MACC) is an indispensable tool for planning mitigation pathways, but has historically not relied upon robust experimental analysis making it notional at best nor has it included a view of adaptation pathways. This study utilizes a newly developed, medium-density residential community in Vancouver, British Columbia, Canada as a case study for developing a pathway-based MACC. Multiple mitigation and adaptation measures are modeled individually and through exhaustive combination to test their sensitivity on marginal abatement cost and residual cost of climate change. Several visualizations are created to demonstrate several ways of analyzing the resulting large set of data.

@@

This study integrates several climate adaptation strategies into the urban-scale energy simulation process. Adaptation strategies are evaluated on the basis of marginal costs of mitigation \textit{and} adaptation, vis-a-vis the influence of individual design strategies on the resilience of the urban development to expected climate change. This study will simulate the performance of eight climate mitigation and adaptation strategies alongside one urban development trajectory and two climate change scenarios. The simulations will be also carried out at two individual time periods (2050 and 2080), for a case study community in southwestern Canada: Wesbrook Village, Vancouver, British Columbia (BC). A baseline urban building energy model (UBEM) was created to represent the development of the community to-date.

@@

\begin{figure*}[hbpt]
    \centering
    \includegraphics[scale=0.50]{figures/wesbrook_plan.eps}
    \caption{The baseline UBEM for Wesbrook Village in BC.}
    \label{fig:wesbrook_base}
\end{figure*}

@@

\begin{table*}[ht]
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
    \caption{Each strategy as it was applied in the simulations.}
    \footnotesize
    \label{tab:strategies}
    \centering
    % \begin{tabularx}{\textwidth}{|X|X|X|}
    \begin{tabularx}{\linewidth}{|>{\hsize=0.2\hsize}X|
                              >{\hsize=0.5\hsize}X|
                              >{\hsize=0.3\hsize}X|}
        \hline
        \bf{Strategy} & \bf{Description} & \bf{Scale} \\
        \hline
        Adjust Comfort Threshold & Raise cooling setpoints 1C and reduce heating setpoints 1C & All Buildings \\
        \hline
        Green Roof & Install green roofs for insulative, albedo, and heat gain benefits. & All Buildings \\
        \hline
        Deep Envelope and HVAC Retrofit & Install heat pumps for space heating and DHW along with high performance shells and reduced window-wall ratios & Existing Buildings \\
        \hline
        Passive House & Require passive house building codes for envelope. & New Buildings \\
        \hline
        Heat Pumps & Install heat pumps for space heating, cooling and DHW. & All buildings \\
        \hline
        Mass Timber & Construction must utilize mass timber. & New Buildings \\
        \hline
        Seawater Cooling Loop & Buildings get space cooling from heat pump that is amplified with a seawater cooling loop & All Buildings \\
        \hline
        Rooftop Photovoltaic & Install grid-tied rooftop solar with net-metering & All Buildings \\
        \hline
    \end{tabularx}
    \vspace{-5pt}   % Please use appropriate negative vspace to remove the space above/belovw the Table
\end{table*}

@@

The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{cwec_2016} was morphed, following the algorithms set out by \citet{belcher_constructing_2005} and expanded upon by \citet{jentsch_climate_2008}. Two climate pathways are followed, discussed in this paper as the \textit{best-case} and \textit{worst-case} scenarios. These are \textit{Shared Socioeconomic Pathway 1} (SSP126) and \textit{Shared Socioeconomic Pathway 5} (SSP585)
defined in \citet{oneill_roads_2017}. Two morphed climate files were produced at 2050 and 2080 for each pathway.

% and described in Figure \ref{fig:weatherfiles}.

@@

Adaptation was considered as the capacity of a building to remain within its comfort threshold while also mitigating carbon emissions. The threshold considered is between 18\textdegree C and 26\textdegree C. For each building in each strategy-set the total amount of hours that interior temperature exceeds the threshold is counted. The median value from the buildings is then taken as the adaptation metric for each strategy-set.

@@

\subsection*{Total Annualized Cost}
Components and technology costs was gathered through several data sources, \citep{noauthor_cpcn_2014,schlueter_3for2_2016,salasovich_energy_2016,kegel_life_nodate,gordian_rsmeans_2020}. Cost is a highly uncertain data point to incorporate into building energy models. Cost is assessed as the net difference between a strategy-set and the baseline, each calculated as the 30-year total annualized cost (TAC) from within the City Energy Analyst, applying a 5\% discount rate.

\subsection*{Operational and embodied carbon}
Operational carbon is taken as the carbon emitted over a 30 year period from each building as a result of energy consumption for plug-load, heating and cooling, and ventilation service. BC's electrical grid is served by a hydroelectric power provider and is a low-carbon source, at 10.8 kgCO2e/kWh \citep{bc_ministry_of_envrionmetn_and_climate_change_strategy_bc_2019}. The district heating provider intends for the system tobe  fed entirely from natural gas boilers until 2023 at which point the transition to a more complex system of natural gas peaking boilers and electric heat pumps. This system was previously modelled in \citet{mccarty_accepted_2020}. Its carbon intensity was estimated to be between an annual average of 10.8 and 180.0 kgCO2e/kWh. The range is due to fluctuations in the amount of natural gas used in the system, as well as the amount of waste heat available to create a more efficient lift in the heat pumps. Limits imposed on heat pump and waste heat capacity are drawn from the operator in \citet{noauthor_infrastructure_2014}.

@@

%---------------------------------------------------------------------------------------
\section*{Results}
\begin{figure}[h!]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.8]{figures/general_results_box.eps}
    \caption{General results from the iterations presented across total emissions over 30 years and net 30-year total annualized cost.}
    \label{fig:cross_plot}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[scale=1.15]{figures/district_heat_charts.eps}
    \caption{Comparing the demand on the partially natural gas fed district heat system across the baseline scenarios in the end of century best- (SSP126) and worst-case (SSP585) scenarios. The highlighted gap between the two curves shows where less natural gas was used in the SSP585 scenario.}
    \label{fig:compare_district}
\end{figure}

@@

% Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario. For each of the four combinations of development and climate change pathway, %Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier. The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%. The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented. These charts can inform the creation of a \textit{true} MACC by informing which strategy set is chosen based on not only marginal abatement cost, but also the adaptation metric.

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set is \textit{00011111}.

% is highlighted in Figure \ref{fig:pareto_plot}.

Figure \ref{fig:true_macc_both} describes how each strategy contributes to the overall decrease in emissions. The MACC is shown in Figure \ref{fig:true_macc_both} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction. This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity. The majority of the abatement can be attributed to the heat pump strategy, removing natural gas from the fuel mix, while the other strategies can be said to lending to adaptability. This point about the fuel mix will be returned to more in the discussion, but raises that question about how to affordably meet zero-carbon targets after fuel-switching has been achieved. This scenario only achieves 67\% emissions reduction over the baseline by 2080.

@@

%\begin{figure}[t]
%    \centering
%    \captionsetup{margin=.5cm}
%    \includegraphics[scale=0.50]{figures/pareto_plots_585_box.eps}
%    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
%    \label{fig:pareto_plot}
%\end{figure}

%---------------------------------------------------------------------------------------
\section*{Discussion}

\subsection*{Abatement after fuel-switching}
The context for this study sets up an interesting proposition within BC. Electricity in BC is provided primarily via hydroelectricity. Emissions within the building sector are therefore driven by natural gas use, either on-site or within district systems. The two \textit{true} MACC cases show that in order to reach large reductions over the baseline condition, the use of natural gas must be eliminated. This however raises the point of how abatement should continue once the significant reductions are made and systems are then relying on a near-carbon-free grid. At present, BC (and UBC) expects new buildings to be net-zero \textit{energy} ready by the early 2030s, with no clear objectives on whether buildings should be truly net-zero energy (NZE) in a more distant future. There is reason for this, as evidenced by the modelling undertaken in this work. This study showed that in testing rooftop PV systems for medium density developments, PV systems will not yield large emissions reductions under any scenario. In the worst-case climate scenario rooftop panels alone reduced emissions by only 4.4\%.

%Additionally building-based sequestration methods offer a potential avenue for meeting net-zero \textit{carbon} goals \citep{skullestad_high-rise_2016}. This study did not consider the Mass Timber strategy to be carbon sequestering, but it is less intensive than cement-based building, leading to between 60 and 300 Tonnes of carbon abated, depending on the development scenario.

\subsection*{Limitations of approach}

The first limitation of this study lies in the not-so-explicit temporal interaction of the interventions. Each building was modeled as having its own unique construction and retrofit dates, which contribute to the emissions and total annualized cost profile for each run of the district energy model. While unique in their start and end date they are all set on a 30-year time horizon for all elements replacement. For some building technologies this may be a realistic time horizon for design-life, for many others it is not. Future efforts need to consider equipment and technology replacements more actively while also engaging the temporal simulation steps at more fine scales, possibly ten-years.

A major limitation in the framework underpinning this study is the finite space of strategy choice. We test eight strategies here that are applied generally across the district. This may not always be a problem if prior to the study a strategy evaluation is conducted or subject-matter experts are brought in to help establish priors. Future efforts need to be more precise with strategy implementation based on building or site need.

%---------------------------------------------------------------------------------------
\section*{Conclusion}
In this study the output of 1024 different urban building energy simulations was used to generate marginal abatement cost curves and complimentary visualizations to make decisions on climate mitigation and adaptation at an urban scale. A case study of Wesbrook Village, a planend 25,000-member residential community in Vancouver, Canada was used.

The resulting MACCs were created from two perspectives. First the \textit{illustrative} MACCs (Figures \ref{fig:MACC_threshold} and \ref{fig:MACC_budget}) sought to provide general guidance on which strategies achieve targeted mitigation under different planning constraints. The \textit{true} MACCs (Figure \ref{fig:true_macc_both}) reveal how the individual strategies within a set interact technically and financially to ultimately abate a certain amount of carbon. The candidate for the one of the \textit{true} MACCs was selected based on a mixture of adaptation and mitigation criteria.

% using a plot of pareto optimums (Figure \ref{fig:pareto_plot}). This enables planners to begin to assess adaptation targets alongside abatement.
